Identifying Factors That Affect Political Freedom Within the OECD

### 2020-11-25 paper/paper.tex
fixed issue

\title{Identifying Factors That Affect Political Freedom Within the OECD}
\author{Joe Despres\textsuperscript{1}, Sabrina Ball\textsuperscript{1}, Jacob Haywood\textsuperscript{1}, \& Joe Sigler\textsuperscript{1}}
\date{Last compiled 20:41}

@@

\begin{longtable}[t]{lrrrrrr}
\caption{\label{tab:unnamed-chunk-1}Descriptive Statistics}\\
\toprule
Variable & Mean & Median & Std & Min & Max & Range\\
\midrule
Political Rights & 6.60 & 7.00 & 0.79 & 2.00 & 7.00 & 5.00\\
Year & 2009.50 & 2009.50 & 5.19 & 2001.00 & 2018.00 & 17.00\\
Corruption Perception & 31.95 & 29.00 & 15.87 & 8.00 & 71.00 & 63.00\\
Education Expenditure & 0.20 & 0.20 & 0.04 & 0.10 & 0.37 & 0.27\\
Electricity Use & 8682.17 & 6695.00 & 7533.32 & 866.00 & 54800.00 & 53934.00\\
\addlinespace
Gini & 33.77 & 32.70 & 6.35 & 24.40 & 56.80 & 32.40\\
Internet Users & 65.41 & 70.90 & 22.93 & 2.85 & 99.00 & 96.15\\
Life Expectancy & 0.60 & 0.61 & 0.06 & 0.45 & 0.78 & 0.33\\
Labor Force Participation & 79.30 & 80.00 & 2.84 & 70.20 & 84.40 & 14.20\\
Military Spending & 1.68 & 1.41 & 1.16 & 0.00 & 8.54 & 8.54\\
\addlinespace
Murders rate & 3.13 & 1.04 & 6.15 & 0.15 & 29.07 & 28.92\\
\bottomrule
\end{longtable}

@@

\begin{figure}
\includegraphics[width=0.5\linewidth]{paper_files/figure-latex/unnamed-chunk-2-1} \includegraphics[width=0.5\linewidth]{paper_files/figure-latex/unnamed-chunk-2-2} \caption{ }\label{fig:unnamed-chunk-2}
\end{figure}

@@

From the best subsets, it was appropriate to narrow our model choices down to three. First, the model with six degrees of freedom, next one with five, and one with four. The results from these three models is in Table 2 made using Stargazer (Hlavac, 2018) on the next page. The model with six degrees of freedom contains \textbf{Internet Users} which is 0.001, which is not statistically significant and even if it was a one percent increase in the percentage of people using the internet associated with a 0.001 increase in political freedom is not politically significant in any meaningful way. Looking at the model with five degrees of freedom, all of our coefficients are statistically significant at \(p < 0.01\). The model with four degrees of freedom also has statistically significant coefficients and we would pick it had life expectancy not been significant. Counterintuitively, politically freedom seems to decrease as life expectancy increases. We are not qualified to attempt explain that we can only speculate. We are going to choose the model with five degrees of freedom. So we arrived at the following model.\\
Double spacing makes this dificult
\[\operatorname{polrights\_fh} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) + \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\]
\[ \beta_{3}(\operatorname{life\_expectancy\_years}) + \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) + \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon\]
\includegraphics{paper_files/figure-latex/unnamed-chunk-4-1.pdf}
The scatter plots look a bit strange at first because of the nature of the discrete response variable. However, this does seem to fit the data reasonably. There is a fairly linear relationship with a clear sloping line which, accept for life expectancy, concur with the regression coeffeceintes.

@@

\begin{figure}
\includegraphics[width=0.5\linewidth]{paper_files/figure-latex/unnamed-chunk-5-1} \includegraphics[width=0.5\linewidth]{paper_files/figure-latex/unnamed-chunk-5-2} \caption{ }\label{fig:unnamed-chunk-5}
\end{figure}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(tidyverse)}
\KeywordTok{library}\NormalTok{(kableExtra)}
\KeywordTok{library}\NormalTok{(stargazer)}
\KeywordTok{library}\NormalTok{(patchwork)}
\NormalTok{size \textless{}{-}}\StringTok{ }\DecValTok{30}

@@

\NormalTok{data \textless{}{-}}\StringTok{ }\NormalTok{readr}\OperatorTok{::}\KeywordTok{read\_csv}\NormalTok{(here}\OperatorTok{::}\KeywordTok{here}\NormalTok{(}\StringTok{"data"}\NormalTok{, }\StringTok{"df.csv"}\NormalTok{)) }
\NormalTok{subsets \textless{}{-}}\StringTok{ }\NormalTok{readr}\OperatorTok{::}\KeywordTok{read\_csv}\NormalTok{(here}\OperatorTok{::}\KeywordTok{here}\NormalTok{(}\StringTok{"data"}\NormalTok{, }\StringTok{"subsets.csv"}\NormalTok{))}
\NormalTok{model\_df6\_formula \textless{}{-}}\StringTok{ }\NormalTok{subsets }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{filter}\NormalTok{(df }\OperatorTok{==}\StringTok{ }\DecValTok{6}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{arrange}\NormalTok{(}\KeywordTok{desc}\NormalTok{(adj.r.squared)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(model) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{head}\NormalTok{(}\DecValTok{1}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{as.character}\NormalTok{() }

@@

\NormalTok{fit\_df4 \textless{}{-}}\StringTok{ }\KeywordTok{lm}\NormalTok{(model\_df4\_formula, data)}
\NormalTok{stat \textless{}{-}}\StringTok{ }\ControlFlowTok{function}\NormalTok{(}\DataTypeTok{df =}\NormalTok{ data, x, }\DataTypeTok{rounding\_digits =} \DecValTok{2}\NormalTok{)\{}

\NormalTok{    x \textless{}{-}}\StringTok{ }\NormalTok{dplyr}\OperatorTok{::}\KeywordTok{enquo}\NormalTok{(x)}
\NormalTok{    df }\OperatorTok{\%\textgreater{}\%}
\StringTok{      }\NormalTok{dplyr}\OperatorTok{::}\KeywordTok{summarise}\NormalTok{(}
                       \DataTypeTok{Mean  =} \KeywordTok{mean}\NormalTok{( }\OperatorTok{!!}\StringTok{ }\NormalTok{x),}
                     \DataTypeTok{Median  =} \KeywordTok{median}\NormalTok{( }\OperatorTok{!!}\StringTok{ }\NormalTok{x),}
                         \DataTypeTok{Std =} \KeywordTok{sd}\NormalTok{  ( }\OperatorTok{!!}\StringTok{ }\NormalTok{x),}
                         \DataTypeTok{Min =} \KeywordTok{min}\NormalTok{ ( }\OperatorTok{!!}\StringTok{ }\NormalTok{x),}
                         \DataTypeTok{Max =} \KeywordTok{max}\NormalTok{ ( }\OperatorTok{!!}\StringTok{ }\NormalTok{x),}
                       \DataTypeTok{Range =} \KeywordTok{max}\NormalTok{(}\OperatorTok{!!}\StringTok{ }\NormalTok{x) }\OperatorTok{{-}}\StringTok{ }\KeywordTok{min}\NormalTok{(}\OperatorTok{!!}\StringTok{ }\NormalTok{x) ) }\OperatorTok{\%\textgreater{}\%}
\StringTok{      }\NormalTok{dplyr}\OperatorTok{::}\KeywordTok{mutate\_if}\NormalTok{(is.numeric, round, rounding\_digits)}
\NormalTok{  \}}

\NormalTok{data }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\OperatorTok{{-}}\NormalTok{country) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\KeywordTok{map}\NormalTok{(}\ControlFlowTok{function}\NormalTok{(x)\{}\KeywordTok{stat}\NormalTok{(x, }\DataTypeTok{df =}\NormalTok{ data)\}) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{bind\_rows}\NormalTok{(}\DataTypeTok{.id =} \StringTok{"Variable"}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Variable =} \KeywordTok{replace}\NormalTok{(Variable, }
                            \DataTypeTok{values =} \KeywordTok{c}\NormalTok{(}\StringTok{"Political Rights"}\NormalTok{, }\StringTok{"Year"}\NormalTok{, }
                                       \StringTok{"Corruption Perception"}\NormalTok{, }
                                       \StringTok{"Education Expenditure"}\NormalTok{, }
                                       \StringTok{"Electricity Use"}\NormalTok{, }
                                       \StringTok{"Gini"}\NormalTok{, }
                                       \StringTok{"Internet Users"}\NormalTok{,}
                                       \StringTok{"Life Expectancy"}\NormalTok{, }
                                       \StringTok{"Labor Force Participation"}\NormalTok{, }
                                       \StringTok{"Military Spending"}\NormalTok{, }
                                       \StringTok{"Murders rate"}\NormalTok{))) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\KeywordTok{kable}\NormalTok{(}
  \DataTypeTok{format =} \StringTok{"latex"}\NormalTok{,}
  \DataTypeTok{booktabs =} \OtherTok{TRUE}\NormalTok{,}
  \DataTypeTok{escape =} \OtherTok{FALSE}\NormalTok{,}
  \DataTypeTok{longtable =} \OtherTok{TRUE}\NormalTok{,}
 \DataTypeTok{caption =} \StringTok{"Descriptive Statistics"}\NormalTok{)}
\NormalTok{r \textless{}{-}}\StringTok{ }\NormalTok{subsets }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{group\_by}\NormalTok{(df) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{summarise}\NormalTok{(}\DataTypeTok{adj =} \KeywordTok{max}\NormalTok{(adj.r.squared, }\DataTypeTok{na.rm =}\NormalTok{ T))}

>>>>

\title{Identifying Factors That Affect Political Freedom Within the OECD}
\author{Joe Despres\textsuperscript{1}, Sabrina Ball\textsuperscript{1}, Jacob Haywood\textsuperscript{1}, \& Joe Sigler\textsuperscript{1}}
\date{Last compiled 21:15}

@@

\begin{longtable}[t]{lrrrrrr}
\caption{\label{tab:unnamed-chunk-2}Descriptive Statistics}\\
\toprule
Variable & Mean & Median & Std & Min & Max & Range\\
\midrule
Political Rights & 6.60 & 7.00 & 0.79 & 2.00 & 7.00 & 5.00\\
Year & 2009.50 & 2009.50 & 5.19 & 2001.00 & 2018.00 & 17.00\\
Corruption Perception & 31.95 & 29.00 & 15.87 & 8.00 & 71.00 & 63.00\\
Education Expenditure & 0.20 & 0.20 & 0.04 & 0.10 & 0.37 & 0.27\\
Electricity Use & 8682.17 & 6695.00 & 7533.32 & 866.00 & 54800.00 & 53934.00\\
\addlinespace
Gini & 33.77 & 32.70 & 6.35 & 24.40 & 56.80 & 32.40\\
Internet Users & 65.41 & 70.90 & 22.93 & 2.85 & 99.00 & 96.15\\
Life Expectancy & 0.60 & 0.61 & 0.06 & 0.45 & 0.78 & 0.33\\
Labor Force Participation & 79.30 & 80.00 & 2.84 & 70.20 & 84.40 & 14.20\\
Military Spending & 1.68 & 1.41 & 1.16 & 0.00 & 8.54 & 8.54\\
\addlinespace
Murders rate & 3.13 & 1.04 & 6.15 & 0.15 & 29.07 & 28.92\\
\bottomrule
\end{longtable}

@@

\begin{figure}
\includegraphics[width=0.5\linewidth]{paper_files/figure-latex/unnamed-chunk-3-1} \includegraphics[width=0.5\linewidth]{paper_files/figure-latex/unnamed-chunk-3-2} \caption{ }\label{fig:unnamed-chunk-3}
\end{figure}

@@

From the best subsets, it was appropriate to narrow our model choices down to three. First, the model with six degrees of freedom, next one with five, and one with four. The results from these three models is in Table 2 made using Stargazer (Hlavac, 2018) on the next page. The model with six degrees of freedom contains \textbf{Internet Users} which is 0.001, which is not statistically significant and even if it was a one percent increase in the percentage of people using the internet associated with a 0.001 increase in political freedom is not politically significant in any meaningful way. Looking at the model with five degrees of freedom, all of our coefficients are statistically significant at \(p < 0.01\). The model with four degrees of freedom also has statistically significant coefficients and we would pick it had life expectancy not been significant. Counterintuitively, politically freedom seems to decrease as life expectancy increases. We are not qualified to attempt explain that we can only speculate. We are going to choose the model with five degrees of freedom. So we arrived at the following model.\\
Double spacing makes this dificult
\[\operatorname{polrights\_fh} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) + \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\]
\[ \beta_{3}(\operatorname{life\_expectancy\_years}) + \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) + \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon\]
\includegraphics{paper_files/figure-latex/unnamed-chunk-5-1.pdf}
The scatter plots look a bit strange at first because of the nature of the discrete response variable. However, this does seem to fit the data reasonably. There is a fairly linear relationship with a clear sloping line which, accept for life expectancy, concur with the regression coeffeceintes.

@@

\begin{figure}
\includegraphics[width=0.5\linewidth]{paper_files/figure-latex/unnamed-chunk-6-1} \includegraphics[width=0.5\linewidth]{paper_files/figure-latex/unnamed-chunk-6-2} \caption{ }\label{fig:unnamed-chunk-6}
\end{figure}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(tidyverse)}
\KeywordTok{library}\NormalTok{(kableExtra)}
\KeywordTok{library}\NormalTok{(stargazer)}
\KeywordTok{library}\NormalTok{(patchwork)}

\NormalTok{size \textless{}{-}}\StringTok{ }\DecValTok{30}

@@

\CommentTok{\# Read and Clean {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}
\NormalTok{files \textless{}{-}}\StringTok{ }\KeywordTok{list.files}\NormalTok{(}\DataTypeTok{path =}\NormalTok{ here}\OperatorTok{::}\KeywordTok{here}\NormalTok{(}\StringTok{"raw\_data"}\NormalTok{), }\DataTypeTok{pattern =} \StringTok{".csv"}\NormalTok{)}

\NormalTok{cleaning \textless{}{-}}\StringTok{ }\ControlFlowTok{function}\NormalTok{(df)\{}
\NormalTok{  df \textless{}{-}}\StringTok{ }\KeywordTok{pivot\_longer}\NormalTok{(df, }\DataTypeTok{cols =} \OperatorTok{{-}}\NormalTok{country, }\DataTypeTok{names\_to =} \StringTok{"year"}\NormalTok{)}
\NormalTok{\}}

\NormalTok{data \textless{}{-}}\StringTok{ }\NormalTok{files }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{map}\NormalTok{(}\ControlFlowTok{function}\NormalTok{(x) }\KeywordTok{read\_csv}\NormalTok{(}\KeywordTok{paste0}\NormalTok{(}\StringTok{"raw\_data/"}\NormalTok{, x))) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{setNames}\NormalTok{(}\KeywordTok{gsub}\NormalTok{(}\StringTok{"}\CharTok{\textbackslash{}\textbackslash{}}\StringTok{.csv$"}\NormalTok{, }\StringTok{""}\NormalTok{, files)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{map}\NormalTok{(cleaning) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{bind\_rows}\NormalTok{(}\DataTypeTok{.id =} \StringTok{"id"}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{pivot\_wider}\NormalTok{(}\DataTypeTok{names\_from =}\NormalTok{ id)}

\CommentTok{\# Filtering {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}

\NormalTok{countries \textless{}{-}}\StringTok{ }\KeywordTok{readRDS}\NormalTok{(here}\OperatorTok{::}\KeywordTok{here}\NormalTok{(}\StringTok{"data"}\NormalTok{, }\StringTok{"countries.RDS"}\NormalTok{))}

\NormalTok{data \textless{}{-}}\StringTok{ }\NormalTok{data }\OperatorTok{\%\textgreater{}\%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(year }\OperatorTok{\textgreater{}}\StringTok{ }\DecValTok{2000}\NormalTok{, year }\OperatorTok{\textless{}}\StringTok{ }\DecValTok{2019}\NormalTok{, country }\OperatorTok{\%in\%}\StringTok{ }\NormalTok{countries) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{group\_by}\NormalTok{(country) }\OperatorTok{\%\textgreater{}\%}
\StringTok{  }\KeywordTok{mutate\_at}\NormalTok{(}\KeywordTok{vars}\NormalTok{(}\OperatorTok{{-}}\NormalTok{country),}\KeywordTok{list}\NormalTok{(}\OperatorTok{\textasciitilde{}}\KeywordTok{ifelse}\NormalTok{(}\KeywordTok{is.na}\NormalTok{(.), }\KeywordTok{median}\NormalTok{(., }\DataTypeTok{na.rm =} \OtherTok{TRUE}\NormalTok{), .))) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\CommentTok{\# Iceland spent 0 so I needed to manually recode that}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{military\_spending\_pct\_of\_gdp =} \KeywordTok{replace\_na}\NormalTok{(military\_spending\_pct\_of\_gdp, }\DecValTok{0}\NormalTok{), }
         \DataTypeTok{year =} \KeywordTok{as.numeric}\NormalTok{(year)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{murder\_per\_mil\_people =} \KeywordTok{replace}\NormalTok{(murder\_per\_mil\_people, country }\OperatorTok{==}\StringTok{ "Mexico"}\NormalTok{, }\FloatTok{29.07}\NormalTok{),}
         \DataTypeTok{murder\_per\_mil\_people =} \KeywordTok{replace}\NormalTok{(murder\_per\_mil\_people, country }\OperatorTok{==}\StringTok{ "Chile"}\NormalTok{, }\FloatTok{4.4}\NormalTok{),}
         \DataTypeTok{murder\_per\_mil\_people =} \KeywordTok{replace}\NormalTok{(murder\_per\_mil\_people, country }\OperatorTok{==}\StringTok{ "Colombia"}\NormalTok{, }\FloatTok{25.34}\NormalTok{)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{         }\CommentTok{\# https://en.wikipedia.org/wiki/List\_of\_countries\_by\_intentional\_homicide\_rate}
\StringTok{         }\CommentTok{\# these murder rates were not included in the gapminder but i didnt want to }
\StringTok{         }\CommentTok{\# lose 3 important countries in LA}
\StringTok{  }\KeywordTok{relocate}\NormalTok{(polrights\_fh) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{polrights\_fh =}\NormalTok{ (}\DecValTok{8} \OperatorTok{{-}}\StringTok{ }\NormalTok{polrights\_fh),}
                                    \DataTypeTok{military\_spending\_pct\_of\_gdp =}\NormalTok{ military\_spending\_pct\_of\_gdp }\OperatorTok{*}\StringTok{ }\DecValTok{100}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{corruption\_perception\_index\_cpi =}\NormalTok{ (corruption\_perception\_index\_cpi }\OperatorTok{{-}}\StringTok{ }\DecValTok{100}\NormalTok{) }\OperatorTok{*}\StringTok{ }\DecValTok{{-}1}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{ungroup}\NormalTok{()}

\CommentTok{\# Best Subset Selection {-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}{-}}

\NormalTok{vars \textless{}{-}}\StringTok{ }\NormalTok{data }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\OperatorTok{{-}}\NormalTok{country, }\OperatorTok{{-}}\NormalTok{year, }\OperatorTok{{-}}\KeywordTok{ends\_with}\NormalTok{(}\StringTok{"\_fh"}\NormalTok{)) }\OperatorTok{\%\textgreater{}\%}
\StringTok{  }\KeywordTok{names}\NormalTok{()}

\NormalTok{outcome \textless{}{-}}\StringTok{ "polrights\_fh"}

\NormalTok{models \textless{}{-}}\StringTok{ }\KeywordTok{list}\NormalTok{()}
\ControlFlowTok{for}\NormalTok{ (i }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(vars)) \{}
\NormalTok{  vc \textless{}{-}}\StringTok{ }\KeywordTok{combn}\NormalTok{(vars,i)}
  \ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\KeywordTok{ncol}\NormalTok{(vc)) \{}
\NormalTok{    model \textless{}{-}}\StringTok{ }\KeywordTok{as.formula}\NormalTok{(}\KeywordTok{paste0}\NormalTok{(outcome, }\StringTok{" \textasciitilde{}"}\NormalTok{, }\KeywordTok{paste0}\NormalTok{(vc[,j], }\DataTypeTok{collapse =} \StringTok{" + "}\NormalTok{)))}
\NormalTok{    models \textless{}{-}}\StringTok{ }\KeywordTok{c}\NormalTok{(models, model)}

\NormalTok{    \}}
\NormalTok{  \}}

\NormalTok{subsets \textless{}{-}}\StringTok{ }\KeywordTok{map}\NormalTok{(models, }\ControlFlowTok{function}\NormalTok{(x) }\KeywordTok{lm}\NormalTok{(x, data)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{map}\NormalTok{(broom}\OperatorTok{::}\NormalTok{glance) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{setNames}\NormalTok{(models) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{bind\_rows}\NormalTok{(}\DataTypeTok{.id =} \StringTok{"id"}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{distinct}\NormalTok{() }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{model =}\NormalTok{ id) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}
    \DataTypeTok{Model =} \KeywordTok{str\_replace\_all}\NormalTok{(model, }\StringTok{"\_"}\NormalTok{, }\StringTok{" "}\NormalTok{),}
    \DataTypeTok{Model =} \KeywordTok{str\_replace}\NormalTok{(Model, }\StringTok{"\textasciitilde{}"}\NormalTok{, }\StringTok{"="}\NormalTok{), }
    \DataTypeTok{Model =} \KeywordTok{str\_to\_title}\NormalTok{(Model))}
\NormalTok{model\_df6\_formula \textless{}{-}}\StringTok{ }\NormalTok{subsets }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{filter}\NormalTok{(df }\OperatorTok{==}\StringTok{ }\DecValTok{6}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{arrange}\NormalTok{(}\KeywordTok{desc}\NormalTok{(adj.r.squared)) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(model) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{head}\NormalTok{(}\DecValTok{1}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }\KeywordTok{as.character}\NormalTok{() }

@@

\NormalTok{fit\_df4 \textless{}{-}}\StringTok{ }\KeywordTok{lm}\NormalTok{(model\_df4\_formula, data)}
\NormalTok{stat \textless{}{-}}\StringTok{ }\ControlFlowTok{function}\NormalTok{(x, }\DataTypeTok{df =}\NormalTok{ data, }\DataTypeTok{rounding\_digits =} \DecValTok{2}\NormalTok{)\{}

\NormalTok{    x \textless{}{-}}\StringTok{ }\KeywordTok{enquo}\NormalTok{(x)}
\NormalTok{    df }\OperatorTok{\%\textgreater{}\%}
\StringTok{      }\KeywordTok{summarise}\NormalTok{(}
                       \DataTypeTok{Mean  =} \KeywordTok{mean}\NormalTok{( }\OperatorTok{!!}\StringTok{ }\NormalTok{x),}
                     \DataTypeTok{Median  =} \KeywordTok{median}\NormalTok{( }\OperatorTok{!!}\StringTok{ }\NormalTok{x),}
                         \DataTypeTok{Std =} \KeywordTok{sd}\NormalTok{  ( }\OperatorTok{!!}\StringTok{ }\NormalTok{x),}
                         \DataTypeTok{Min =} \KeywordTok{min}\NormalTok{ ( }\OperatorTok{!!}\StringTok{ }\NormalTok{x),}
                         \DataTypeTok{Max =} \KeywordTok{max}\NormalTok{ ( }\OperatorTok{!!}\StringTok{ }\NormalTok{x),}
                       \DataTypeTok{Range =} \KeywordTok{max}\NormalTok{(}\OperatorTok{!!}\StringTok{ }\NormalTok{x) }\OperatorTok{{-}}\StringTok{ }\KeywordTok{min}\NormalTok{(}\OperatorTok{!!}\StringTok{ }\NormalTok{x) ) }\OperatorTok{\%\textgreater{}\%}
\StringTok{      }\KeywordTok{mutate\_if}\NormalTok{(is.numeric, round, rounding\_digits)}
\NormalTok{\}}

\NormalTok{data }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\OperatorTok{{-}}\NormalTok{country) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\KeywordTok{map}\NormalTok{(}\ControlFlowTok{function}\NormalTok{(x)\{}\KeywordTok{stat}\NormalTok{(x)\}) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{bind\_rows}\NormalTok{(}\DataTypeTok{.id =} \StringTok{"Variable"}\NormalTok{) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Variable =} \KeywordTok{replace}\NormalTok{(Variable, }
                            \DataTypeTok{values =} \KeywordTok{c}\NormalTok{(}\StringTok{"Political Rights"}\NormalTok{, }\StringTok{"Year"}\NormalTok{, }
                                       \StringTok{"Corruption Perception"}\NormalTok{, }
                                       \StringTok{"Education Expenditure"}\NormalTok{, }
                                       \StringTok{"Electricity Use"}\NormalTok{, }
                                       \StringTok{"Gini"}\NormalTok{, }
                                       \StringTok{"Internet Users"}\NormalTok{,}
                                       \StringTok{"Life Expectancy"}\NormalTok{, }
                                       \StringTok{"Labor Force Participation"}\NormalTok{, }
                                       \StringTok{"Military Spending"}\NormalTok{, }
                                       \StringTok{"Murders rate"}\NormalTok{))) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\KeywordTok{kable}\NormalTok{(}
  \DataTypeTok{format =} \StringTok{"latex"}\NormalTok{,}
  \DataTypeTok{booktabs =} \OtherTok{TRUE}\NormalTok{,}
  \DataTypeTok{escape =} \OtherTok{FALSE}\NormalTok{,}
  \DataTypeTok{longtable =} \OtherTok{TRUE}\NormalTok{,}
 \DataTypeTok{caption =} \StringTok{"Descriptive Statistics"}\NormalTok{)}
\NormalTok{r \textless{}{-}}\StringTok{ }\NormalTok{subsets }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{group\_by}\NormalTok{(df) }\OperatorTok{\%\textgreater{}\%}\StringTok{ }
\StringTok{  }\KeywordTok{summarise}\NormalTok{(}\DataTypeTok{adj =} \KeywordTok{max}\NormalTok{(adj.r.squared, }\DataTypeTok{na.rm =}\NormalTok{ T))}
